\documentclass[reqno, oneside]{amsart}
\usepackage{etex}
\usepackage{hyperref}

\usepackage{chemarr}
\usepackage{amssymb}
\usepackage{comment}

\usepackage[a4paper]{geometry}


%----------------------------------------------------------------------%


\theoremstyle{definition}
\newtheorem{nul}{}[section]
\newtheorem{dfn}[nul]{Definition}
\newtheorem{axm}[nul]{Axiom}
\newtheorem{rmk}[nul]{Remark}
\newtheorem{term}[nul]{Terminology}
\newtheorem{cnstr}[nul]{Construction}
\newtheorem{ntn}[nul]{Notation}
\newtheorem{exm}[nul]{Example}
\newtheorem{obs}[nul]{Observation}
\newtheorem{ctrexm}[nul]{Counterexample}
\newtheorem{rec}[nul]{Recollection}
\newtheorem{exr}[nul]{Exercise}
\newtheorem{wrn}[nul]{Warning}
\newtheorem{qst}{Question}
\newtheorem*{dfn*}{Definition}
\newtheorem*{axm*}{Axiom}
\newtheorem*{ntn*}{Notation}
\newtheorem*{exm*}{Example}
\newtheorem*{exr*}{Exercise}
\newtheorem*{int*}{Intuition}
\newtheorem*{qst*}{Question}
\newtheorem*{rmk*}{Remark}


\theoremstyle{plain}
\newtheorem{sch}[nul]{Scholium}
\newtheorem{claim}[nul]{Claim}
\newtheorem{thm}[nul]{Theorem}
\newtheorem{prop}[nul]{Proposition}
\newtheorem{lem}[nul]{Lemma}
\newtheorem{var}[nul]{Variant}
\newtheorem{sublem}{Lemma}[nul]
\newtheorem{por}[nul]{Porism}
\newtheorem{cnj}[nul]{Conjecture}
\newtheorem{cor}{Corollary}[nul]
\newtheorem*{thm*}{Theorem}
\newtheorem*{prop*}{Proposition}
\newtheorem*{cor*}{Corollary}
\newtheorem*{lem*}{Lemma}
\newtheorem*{cnj*}{Conjecture}
\newtheorem{innercustomthm}{Theorem}
\newenvironment{customthm}[1]
  {\renewcommand\theinnercustomthm{#1}\innercustomthm}
  {\endinnercustomthm}



%----------------------------------------------------------------------%

\DeclareMathOperator{\Aut}{\text{Aut}}
\DeclareMathOperator{\Tr}{\text{Tr}}
\DeclareMathOperator{\Res}{\text{Res}}
\DeclareMathOperator{\im}{\text{im}}
\DeclareMathOperator*{\colim}{\mathrm{colim}}
\DeclareMathOperator{\Map}{\text{Map}}
\DeclareMathOperator{\cofiber}{\text{cofiber}}
\DeclareMathOperator{\fiber}{\text{fiber}}
\DeclareMathOperator{\gr}{\mathrm{gr}}
\DeclareMathOperator{\fib}{\mathrm{fib}}
\DeclareMathOperator{\Hom}{\text{Hom}} 
\DeclareMathOperator{\Skel}{\text{Skel}}
\DeclareMathOperator*{\hocolim}{\text{hocolim}}
\DeclareMathOperator*{\holim}{\text{holim}}
\DeclareMathOperator{\smsh}{\wedge}



\DeclareMathOperator{\C}{\mathcal{C}}
\DeclareMathOperator{\D}{\mathcal{D}}
\DeclareMathOperator{\CP}{\mathbb{CP}}
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\mE}{\mathcal{E}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\m}{\mathfrak{m}}
\DeclareMathOperator{\G}{\mathbb{G}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\cG}{\mathcal{G}}
\DeclareMathOperator{\cF}{\mathcal{F}}
\DeclareMathOperator{\cS}{\mathcal{S}}
\DeclareMathOperator{\Ring}{\textbf{Ring}}
\DeclareMathOperator{\Aff}{\textbf{Aff}}
\DeclareMathOperator{\Ran}{\mathrm{Ran}}
\DeclareMathOperator{\Spec}{\text{Spec}}
\DeclareMathOperator{\Poly}{\text{Poly}}
\DeclareMathOperator{\Fin}{\mathrm{Fin}}
\DeclareMathOperator{\Ext}{\text{Ext}}
\DeclareMathOperator{\nil}{\text{nil}}
\DeclareMathOperator{\fin}{\text{fin}}
\DeclareMathOperator{\Gr}{\mathbf{Gr}}
\DeclareMathOperator{\Fil}{\mathbf{Fil}}
\DeclareMathOperator{\Fun}{\text{Fun}}
\DeclareMathOperator{\Alg}{\mathrm{Alg}}
\DeclareMathOperator{\Sp}{\mathrm{Sp}}
\DeclareMathOperator{\Spaces}{\mathcal{S}}
\DeclareMathOperator{\J}{\mathcal{J}}
\DeclareMathOperator{\Cofil}{\mathbf{Cofil}}

%----------------------------------------------------------------------%

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations}
\usepackage{tikz-cd}

\usepackage{adjustbox}

%----------------------------------------------------------------------%

\hyphenation{Mack-ey mon-oid-al Wald-hau-sen}

%----------------------------------------------------------------------%
%----------------------------------------------------------------------%


\begin{document}

\title{Multiplicative Structure in the Stable Splitting of $\Omega SL_n(\mathbb{C})$}
\author{Jeremy Hahn}
\address{Department of Mathematics, Harvard University, Cambridge, MA 02138}
\email{jhahn01@math.harvard.edu}

\author{Allen Yuan}
\address{Department of Mathematics, Massachusetts Institute of Technology, Cambridge, MA 02139}
\email{alleny@mit.edu}

\begin{abstract}
The space of based loops in $SL_n(\mathbb{C})$, also known as the affine Grassmannian of $SL_n(\mathbb{C})$, admits an $\mathbb{E}_2$ or fusion product.  Work of Mitchell and Richter proves that this based loop space stably splits as an infinite wedge sum.  We prove that the Mitchell--Richter splitting is coherently multiplicative, but not $\mathbb{E}_2$.  Nonetheless, we show that the splitting becomes $\mathbb{E}_2$ after base-change to complex cobordism.  Our proof of the $\mathbb{A}_\infty$ splitting involves on the one hand an analysis of the multiplicative properties of Weiss calculus, and on the other a use of Beilinson--Drinfeld Grassmannians to verify a conjecture of Mahowald and Richter.  Other results are obtained by explicit, obstruction-theoretic computations.
\end{abstract}



%----------------------------------------------------------------------%
%----------------------------------------------------------------------%


\setcounter{tocdepth}{1}
\maketitle

\tableofcontents

\vbadness 5000

%----------------------------------------------------------------------%

\section{Introduction}

\input{Introduction.tex}

\section{Filtered and Graded Ring Spectra} \label{sec:FilGra}

\input{FilteredAndGraded.tex}

\section{Revision Merge}

\input{RevisionMerge.tex}

\section{Jeremy's revision}

\input{JeremyRevision.tex}

\section{Allen's revision}
\begin{comment}
\begin{dfn}
The \textit{Ran space} $\text{Ran}(\mathbb{A}^1)$ is the presheaf that assigns to every $\mathbb{C}$-algebra $R$ the set of non-empty finite subsets of $\text{Spec}(R) \times \mathbb{A}^1$.   The Beilinson--Drinfeld Grassmannian is the presheaf $Gr_{G,Ran}$ that assigns to each $\mathbb{C}$-algebra $R$ the set of triplets $(x,\mathcal{E},\beta)$, where $x \in \text{Ran}(\mathbb{A}^1)(R)$, $\mathcal{E}$ is a $G$-torsor on $\mathbb{A}^1 \times \text{Spec}(R)$, and $\beta$ is a trivialization of $\mathcal{E}$ away from the graph of $x$ in $\text{Spec}(R) \times \mathbb{A}^1 $.
\end{dfn}

%Goals: set up Jacob's theorem: describe Disk algebra, Fact algebra

%Add a remark that describes the Ran space in topology?
%maybe just add a digression section that explains how this machinery works

One thinks of the Beilinson--Drinfeld Grassmannian as fibered over the Ran space.  In other words, for every finite collection of points $I \subset \mathbb{A}^1$, there is a corresponding point $x$ in the Ran space.  The fiber of the Beilinson--Drinfeld Grassmannian over $x$ is the moduli of $G$-bundles on $\mathbb{A}^1$ equipped with a trivialization away from the points in $I$.  This fiber is naturally isomorphic to the product of $|I|$ copies of $Gr_G$.  The multiplication on $Gr_G$ is encoded by degeneration of fibers as points collide in $\mathbb{A}^1$.  For more details, see \cite[\S 3]{Zhu}.

The connection of the above structure with the notion of $\mathbb{E}_2$-algebra in homotopy theory was spelled out explicitly by Jacob Lurie in \cite[\S 5.5]{HA}.  Our next goal is to explain this connection; we refer the reader to \cite[\S 5.5]{HA} for the precise definitions.  

Let $\C$ be a symmetric monoidal $\infty$-category.  In homotopy theory, the notion of an $\mathbb{E}_2$ algebra in $\C$ can be thought of as an object with multiplications parametrized by rectilinear embeddings of disjoint unions of the cube $I^2$ into itself.  In the language of $\infty$-operads, this is the notion of an algebra over the operad $\mathbb{E}_2^{\otimes}$, whose operations correspond to the rectilinear embeddings above.  There is a related $\infty$-operad $\mathrm{Disk}(\mathbb{C})^\otimes$ whose algebras $A$ can be thought of as giving an object $A(D)\in\C$ for each disk $D\subset \mathbb{C}$ and coherent maps $A(D_1)\otimes A(D_2)\otimes \cdots \otimes A(D_k) \to A(D)$ for inclusions $D_1\coprod \cdots \coprod D_n \to D$ of disks. The following theorem relates these to $\mathbb{E}_2$-algebras\footnote{For technical reasons, we will work with the non-unital (abbreviated `$\mathrm{nu}$') variants of $\mathbb{E}_2$ and $\mathrm{Disk}(\mathbb{C})$-algebras from now on.}:

\begin{thm}[Proposition 5.4.5.15, \cite{HA}]\label{thm:lcdisk}
There is a fully faithful functor $\Alg^{\mathrm{nu}}_{\mathbb{E}_2}(\C) \to \Alg^{\mathrm{nu}}_{\mathrm{Disk}(\mathbb{C})}(\C)$ with essential image the full subcategory of $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}$-algebras $A$ which are \emph{locally constant} in the sense that for every embedding $D\hookrightarrow D'$ of disks, the natural map $A(D)\to A(D')$ is an equivalence.  
\end{thm}

There is a dual way to encode an $\mathbb{E}_2$ algebra that has a closer relation to algebraic geometry.  We first explain the situation in topology.  An $\mathbb{E}_2$ algebra 

There is an $\infty$-operad $\mathrm{Fact}(\mathbb{C})^{\otimes}$ whose algebras $A$ are the data of an object $A(U)\in\C$ functorially for every open set $U\subset \mathrm{Ran}(\mathbb{C})$ together with \emph{factorization} maps $A(U)\otimes A(V) \to A(U\times V)$ whenever $U$ and $V$ are independent subsets of $\mathrm{Ran}(\mathbb{C})$.\footnote{The reader unfamiliar with the Ran space can keep in mind the example when $U=\mathrm{Ran}(D_1)$, $V=\mathrm{Ran}(D_2)$ for disjoint disks $D_1,D_2\subset \mathbb{C}$, in which case $U\times V = \mathrm{Ran}(D_1\coprod D_2).$}

The notions of $\mathrm{Fact}(\mathbb{C})$ algebra and $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}$ algebra are closely related.  There is a map of $\infty$-operads $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}^\otimes \to \mathrm{Fact}(\mathbb{C})^\otimes.$  Concretely, this means that one can extract from any $\mathrm{Fact}(\mathbb{C})$ algebra $A$ an underlying $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}$ algebra $\overline{A}$ by the formula $\overline{A}(D) = A(\mathrm{Ran}(D)).$  The following theorem of Lurie describes the relationship more precisely:

\begin{thm}[Theorem 5.5.4.10, \cite{HA}]
Let $\C$ be a symmetric monoidal $\infty$-category which admits all colimits and such that the tensor product preserves colimits separately in each variable.  Then operadic left Kan extension along the functor $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}^\otimes \to \mathrm{Fact}(\mathbb{C})^\otimes$ defines a fully faithful functor $F: \Alg_{\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}}(\C) \to \Alg_{\mathrm{Fact}(\mathbb{C})}(\C)$.  Moreover, $F$ restricts to an equivalence between the full subcategory of locally constant $\mathrm{Disk}(\mathbb{C})_{\mathrm{nu}}$ algebras and the full subcategory of $\mathrm{Fact}(\mathbb{C})$ algebras $A$ which are constructible cosheaves and for which the factorization maps $A(U)\otimes A(V) \to A(U\times V)$ are equivalences.  
\end{thm}

\begin{rmk}
In fact, this theorem will be logically unnecessary for what follows and we include it only for completeness.  As such, we omit the definition of the term \emph{constructible cosheaf}.  
\end{rmk}

We summarize the preceding discussion by drawing the following corollary of Theorem~\ref{thm:lcdisk}:
\begin{cor} \label{cor:E2crit}
Let $\C$ be a symmetric monoidal $\infty$-category and $A \in \C$ be a $\mathrm{Fact}(\mathbb{C})$ algebra.  Suppose that $A$ has the property that for any inclusion $D\subset D' \subset \mathbb{C}$ of disks, the natural map $A(\mathrm{Ran}(D))\to A(\mathrm{Ran}(D'))$ is an equivalence.  Then, for any disk $D\subset \mathbb{C}$, $A(\mathrm{Ran}(D))$ inherits the structure of a non-unital $\mathbb{E}_2$-algebra in $\C$.  
\end{cor}


\begin{thm}
Cite Zhu: BD Gr gives a Fact algebra valued in filtered spaces by taking complex points...need to check this (Allen will add this)
\end{thm}
%By taking complex points, the Beilinson-Drinfeld Grassmannian $Gr_G(\mathbb{A}^1)$ provides an example of a factorizable cosheaf on $Ran(\mathbb{C}).$  (should I 

%fact algebra means that for each open in Ran, you get a thing, and you have these factorization maps.  
%say you knew you had an actual space living over Ran(C)...Gr(C) -> Ran(C).  We need to see the structure of the factorization map; say for every two opens in Ran, how do you get the fact map?  Well, you take the isomorphism "a" from Thm 3.3.3 and you restrict it to those two opens.  
%Q1: what about the higher maps?  Well, you have the cocycle condition so everything is coherent higher up
%Q2: What about the filtration?  That should be Thm 3.1.14

\begin{rmk}
add some remark about how it suffices to define over the colimit
\end{rmk}

We also need the following point-set lemma:

\begin{lem}\label{lem:colimproper}
Let $I$ be a finite indexing category and $\{X_i\}_{i\in I}$ be a diagram of topological spaces indexed by $I$.  Let $X = \colim_{i\in I} X_i$ and suppose $f: Y \to X$ is a map of topological spaces with the property that the natural map $f_i: Y\times_X X_i \to X_i$ is proper.  Then the map $f$ is itself proper.
\end{lem}
\begin{proof}
write some shit or not?
\end{proof}

For any $X\subset \mathbb{C}$, $\mathrm{Ran}^{\leq n}(X)$ is a finite colimit of spaces of the form $X^J$ for a finite set $J$.  By **REF**, the restriction of the Beilinson-Drinfeld Grassmannian over each $X^J$ is proper; we obtain the following corollary of Lemma \ref{lem:colimproper}:

\begin{cor}
Let $X\subset \mathbb{C}$.  Then, the restriction of the Beilinson-Drinfeld Grassmannian $\mathrm{Gr}(X)^{\leq n} \to \mathrm{Ran}^{\leq n}(X)$ is proper.
\end{cor}

\begin{thm}
Let $D\subset \mathbb{C}$ be a disk and $\{x \} \hookrightarrow D$ be a point.  Then, the natural map $\mathrm{Gr}(\{x\}) \to \mathrm{Gr}(D)$ is an equivalence of filtered spaces.  
\end{thm}
\begin{proof}

%reduce to the case of a single filtration (weight) and Ran^{leq n} somehow...

For any $X\subset \mathbb{C}$, $\mathrm{Ran}^{\leq n}(X)$ is a finite colimit of 
%the thing you know is that it's proper over each X^I ; then it should imply that it's proper over any finite colimit...in particular, Ran^{\leq n}(X)



%use the proper base change theorem
\end{proof}


%filtered space mapping to Ran C, call it Gr(C)
%pull back to C^I it's proper


cite Zhu: the fact that the thing is proper: Jeremy - can you do this part?
check that the fiber at a point is the same as the fiber over a disk, simultaneously verifying the hypothesis in Corollary \ref{cor:E2crit} and identifying the filtered space A(Ran(D)) as the fiber over a point, which we know to be $\Omega SU(n)$ with the filtration we're asking for.  

%The connection of the above structure with the notion of $\mathbb{E}_2$-algebra in homotopy theory was spelled out explicitly by Jacob Lurie in \cite[\S 5.5]{HA}.  In the language of Lurie's work, the complex points of the Beilinson--Drinfeld Grassmannian form a factorizable cosheaf, valued in spaces, on $\mathrm{Ran}(\mathbb{C})$.  Lurie proves \cite[Theorem 5.5.4.10]{HA} that this is enough to equip the complex points of $Gr_G$ (namely $\Omega G$) with the structure of a non-unital $\mathbb{E}_2$ algebra.  This in turn makes $\Sigma^{\infty}_+ \Omega G$ into a unital (in fact augmented) $\mathbb{E}_2$-ring spectrum.
*****
It is through the Beilinson--Drinfeld perspective that we can most easily see the interaction of the Schubert filtration on $Gr_G$ with its $\mathbb{E}_2$-algebra structure.  The key point is the fact (see, e.g., \cite[3.1.14]{Zhu}) that, as points collide in the Beilinson--Drinfeld Grassmannian, the fiber $Gr_{G,\le \mu_1} \times Gr_{G,\le \mu_2}$ degenerates to $Gr_{G, \le \mu_1+\mu_2}$.

That is already enough to prove that, for example, the Schubert filtration on $\Sigma^{\infty}_+ \Omega SU(2)$ described in Example \ref{sl2example} is an $\mathbb{E}_2$-filtered spectrum in the sense of Section \ref{sec:FilGra}.  What we will actually want to be $\mathbb{E}_2$, or at least $\mathbb{A}_\infty$, is the James filtration on $\Sigma^{\infty}_+ \Omega SU(2)$.  In general, it turns out that the Schubert filtration on the Beilinson--Drinfeld Grassmannian for $SL_n(\mathbb{C})$ provides only direct access to every $n$th piece of the Bott filtration on $\Sigma^{\infty}_+ \Omega SL_n(\mathbb{C})$.  We will follow Segal \cite{Segal} and access the Bott filtration on $Gr_{SL_n}$ in a somewhat indirect manner, by considering not $Gr_{SL_n}$ but $Gr_{GL_n}$:
\end{comment}


\section{The Bott filtration on \texorpdfstring{$\Omega SU(n)$}{OmegaSU(n)}} \label{sec:MRFil}

\input{MitchellRichterFiltration.tex} 

\section{Multiplicative Aspects of Weiss Calculus} \label{sec:MultWeiss}

\input{MultiplicativeWeiss.tex}

\section{Stable \texorpdfstring{$\mathbb{A}_\infty$}{Aoo} Splittings} \label{sec:AooSplit}

\input{AInfinitySplitting.tex}

\section{\texorpdfstring{$\mathbb{E}_2$}{E2} Splittings in Complex Cobordism} \label{sec:MUE2}

\input{SplitInBordism.tex}

\section{Obstructions to a General \texorpdfstring{$\mathbb{E}_2$}{E2} Splitting} \label{sec:Obstruction}

\input{Obstructions.tex}

\appendix

\section{Further Properties of Day Convolution}\label{app:day}

\input{DayConvolution.tex}

\section{Proof of Theorem \ref{thm:SplitMachine}}\label{app:SplittingMachine}

\input{SplittingMachine.tex}

%\section{Square Zero Algebras}

%\input{SquareZero.tex}








\begin{comment}

We can add this in to a second version of the paper, or perhaps write a small second paper.

\section{Snaith's Construction of Periodic Complex Bordism} \label{sec:SnaithSplitting}

\input{PeriodicComplexBordism.tex}

\section{Miscellaneous stuff here}

It would be nice to at some point deal with showing the associated graded $E_2$ structure of BU is the thom spectrum VMU(n).  I've directly pasted in some writing from a previous argument I claimed, but it definitely uses that $\coprod BU(n)$ is an $E_2$ algebra over $\Z _{\geq 0}$ which I never got straight an actual proof of.  

\begin{prop}The associated graded of $\Sigma^{\infty}_+BU$ is $E_2$ equivalent to the Thom spectrum $\bigvee MU(n).$
\end{prop}
\begin{proof}
Let $R = BU$ with its natural filtration, and let $R^{\oplus} = \coprod BU(n)$ with its natural filtration.  Let $M$ be the ($E_\infty$) filtered spectrum which is $MU(n)$ in degree $n$, and all maps are $0$.  In other words, $\bigvee MU(n)$ with its natural filtration is $I(res(M))$.  

We begin with a filtered $E_\infty$ map $z:R^\oplus \to I(res(M))$ coming from the zero section.  Then, $R^\oplus$ comes with the structure of an $E_2$ algebra over $\Z_{\geq 0}^{fil}$.  In fact, $I(res(M))$  has a trivial structure as an $E_\infty$-algebra over $\Z_{\geq 0}^{fil}$ via the augmentation $\Z_{\geq 0}^{fil}\to S^{0,fil} \to I(res(M))$.  We may then tensor $z$ along the augmentation to get a map of $E_2$ filtered spectra $z':R \to I(res(M))$.  

There is a canonical equivalence $I(res(M)) \otimes \mathbb{A} \simeq M$ because $M$ is in the image of $\mathbb{A} \otimes I(-)$ (that is, all the maps in the filtration of $M$ were zero).  As such, $M$ acquires a canonical structure as an $\mathbb{A}$ algebra such that the map $M \otimes \mathbb{A} \to M$ is a map of $E_2$ rings (in fact I think it's $E_\infty$?).  

Finally, we observe that we may tensor $z'$ with $\mathbb{A}$ and compose with the multiplication map to get an $E_2$ map $R\otimes A \to M \otimes A \to M$ which is the right thing up to homotopy, so it's an equivalence.  
\end{proof}

******  

What is $\Sigma^{\infty}_+ \Omega SU(n)[\beta^{-1}]$, by the way?  Is it related to a periodic version of the $X(n)$-filtration of $MU$??
\end{comment}

\bibliographystyle{alpha}
\bibliography{Bibliography}

\end{document}