In this brief section, we assemble results proved above in order to obtain what is labeled Theorem \ref{thm:MainAoo} in the Introduction:

\begin{thm} \label{thm:MainAooInText}
As an $\mathbb{A}_\infty$-algebra object in filtered spectra, the Bott filtration of $\Sigma^{\infty}_+ \Omega SU(n)$ is equivalent to its associated graded.
\end{thm}

\begin{proof}
The construction of the stable Bott filtration as an $\mathbb{A}_\infty$-filtered spectrum is our Theorem \ref{thm:AooFil}.  According to our Theorem \ref{thm:SplitMachine}, to complete the proof of Theorem \ref{thm:MainAooInText} it suffices to produce an $\mathbb{A}_\infty$-cofiltered spectrum with limit $\Sigma^{\infty}_+ \Omega SU(n)$ and with the property that certain composites are equivalences.

As explained in the Introduction, we follow Arone \cite{Arone} in producing the desired cofiltered spectrum by means of Weiss calculus.  Consider, in the notation of Section \ref{sec:MultWeiss} and particularly Example \ref{ex:aronefunctor}, the functor $$F_V:\mathcal{J} \longrightarrow \textbf{Spectra}$$ given by $F_V(W) = \Sigma^{\infty}_+ \Omega \mathcal{J}(V, V \oplus W)$.  Corollary \ref{cor:aronemonoidal} implies that the Taylor tower of $F_V$, applied to $W$, is an $\mathbb{A}_\infty$-cofiltered spectrum with limit $\Sigma^{\infty}_+ \Omega \mathcal{J}(V,V \oplus W)$.

Specializing to the case $V=\mathbb{C}^{n-1}$, $W=\mathbb{C}$, it is straightforward to see that $\mathcal{J}(\mathbb{C}^{n-1},\mathbb{C}^{n-1} \oplus \mathbb{C})$ is equivalent to $SU(n)$.  Roughly speaking, this is because any embedding of $\mathbb{C}^{n-1}$ into $\mathbb{C}^n$ may be extended in a unique way to an automorphism of $\mathbb{C}^n$ that is unitary of determinant one.  Thus, applying Corollary \ref{cor:aronemonoidal} in the case $V=\mathbb{C}^{n-1}$, $W=\mathbb{C}$ gives an $\mathbb{A}_\infty$-cofiltered spectrum with the desired limit.  To complete the proof of Theorem \ref{thm:MainAooInText} it suffices then to check that certain composites are equivalences.  In fact, one of the main results of \cite{Arone} is that those composites are equivalences (see the proof of \cite[Theorem 1.2]{Arone}).
\end{proof}

\begin{rmk}
Mitchell and Richter constructed \cite{CrabbBarcelona} a filtration not just of $$\Omega SU(n) \simeq \Omega \mathcal{J}(\mathbb{C}^{n-1},\mathbb{C}^n),$$ but also of $\Omega \mathcal{J}(V,V\oplus W)$ for a general $V$ and $W$.  Arone showed in \cite[Theorem 1.2]{Arone} that this Mitchell--Richter filtration always stably splits, and Corollary \ref{cor:aronemonoidal} provides an $\mathbb{A}_\infty$-cofiltered spectrum inducing this splitting.  We do not know, however, whether the Mitchell--Richter filtration is always $\mathbb{A}_\infty$-split. 
\end{rmk}