We study the homotopy type of the affine Grassmannian of $SL_n(\mathbb{C})$, which is equivalent to the space $\Omega SU(n)$ of based loops in $SU(n)$.  There are essentially two such multiplications, one arising from the composition of loops and the other from the group multiplication on $SL_n(\mathbb{C})$.  Together, these two multiplications interact to give $\Omega SU(n)$ the structure of an $\mathbb{E}_2$ or chiral algebra.  In geometric representation theory, this structure is witnessed by the existence of the Beilinson--Drinfeld Grassmannian.

The above products are equivalent up to homotopy, and make $H_*(\Omega SU(n);\mathbb{Z})$ into a graded ring.  To describe this ring, let us first name some of its elements.  For each one-dimensional subspace $V \subset \mathbb{C}^n$, there is a loop $\lambda_V:S^1 \rightarrow U(n)$ given by the formula
$$\lambda_V(z)=\left( \begin{array}{cc} z & 0 \\ 0 & I \end{array} \right),$$
with the matrix presented in terms of the decomposition $\mathbb{C}^n \cong V \oplus V^{\perp}$.  Fixing a particular line $W \subset \mathbb{C}^n$, the construction $V \mapsto \lambda_W^{-1} \cdot \lambda_V$ defines a well-known map
$$\mathbb{CP}^{n-1} \rightarrow \Omega SU(n).$$
For $1 \le i \le n-1$, let $b_i \in H_{2i}(\Omega SU(n);\mathbb{Z})$ denote the image of the generator of $H_{2i}(\mathbb{CP}^{n-1};\mathbb{Z})$.  It is a result of Bott \cite{Bott} that
$$H_*(\Omega SU(n);\mathbb{Z}) \cong \mathbb{Z}[b_1,b_2,\cdots,b_{n-1}],$$
with the latter denoting the polynomial algebra on the classes $b_i$.

Notice, in particular, that $H_*(\Omega SU(n);\mathbb{Z})$ is a \textit{bigraded} ring: in addition to the usual homological grading by $*$, there is a grading by word length (assigning each $b_i$ degree $1$).  In fact, Mahowald observed that the action of the Steenrod algebra on $H_*(\Omega SU(n);\mathbb{F}_2)$ preserves this word length filtration, and he conjectured a geometric splitting to be responsible.  This is indeed the case.  

Mitchell \cite{MitchellSU(n)} (and, independently, Segal \cite{Segal}) constructed a filtration $$* =F_{n,0} \longrightarrow F_{n,1} \longrightarrow F_{n,2}\longrightarrow \cdots \longrightarrow \Omega SU(n)$$ which Mitchell and Richter \cite[Theorem 2.1]{CrabbMitchell} showed splits as an infinite wedge sum after applying suspension spectrum:
$$\Sigma^{\infty}_+ \Omega SU(n) \simeq \bigvee_k \Sigma^{\infty} F_{n,k}/F_{n,k-1} \simeq \mathbb{S} \vee \Sigma^{\infty} \mathbb{CP}^{n-1} \vee \cdots.$$

This filtration is the first object of study in this paper; following Mitchell, we name it the \textit{Bott filtration} of $\Omega SU(n)$.  The first nontrivial filtered piece $F_{n,1}$ is given by the map $\mathbb{CP}^{n-1} \rightarrow \Omega SU(n)$ constructed above.  ***??**For higher $k$, the piece $F_{n,k}$ instead receives a map from $(\CP^{n-1})^k$ which is a resolution of singularities.  

We review the construction of the Bott filtration in Section \ref{sec:MRFil}--it is a subfiltration of the Bruhat ordering on (closures of) Iwahori orbits.

\begin{exm}
In the case $n=2$, the Bott filtration of $\Omega SU(2) \simeq \Omega S^3$ is the classical James filtration of $\Omega \Sigma S^2$.
\end{exm}

We will be interested in the \emph{multiplicative} aspects of this filtration and its splitting.  In Section \ref{sec:FilGra}, we review the symmetric monoidal structures on the ($\infty$)-categories of filtered and graded spectra; they are given by Day convolution.  This allows us to talk about $\E_n$-algebras in filtered and graded spectra, providing the language necessary to state our first main theorem (proven in Section \ref{sec:MRFil}):

\begin{thm} \label{thm:BottIsAoo}
The suspension of the Bott filtration 
$$\mathbb{S} \longrightarrow \Sigma_+^{\infty} \mathbb{CP}^{n-1} \simeq \Sigma_+^{\infty} F_{n,1} \longrightarrow \Sigma_+^{\infty} F_{n,2} \longrightarrow \cdots \longrightarrow \Sigma^{\infty}_+ \Omega SU(n).$$
is an $\mathbb{A}_\infty$-algebra object in filtered spectra.
\end{thm}

\begin{rmk}
The Bott filtration is multiplicative before suspension, but for technical reasons we prefer to phrase our results in terms of filtered spectra instead of filtered spaces.
\end{rmk}

\begin{qst} \label{qst:BottE2}
Is the Bott filtration an $\mathbb{E}_2$ filtration?  We do not know the answer--for some thoughts about the problem, see Remark \ref{rmk:E2fil}.
\end{qst}

The proof of Theorem \ref{thm:BottIsAoo} is fairly straightforward, once given access to the sophisticated machinery behind the Beilinson--Drinfeld Grassmannian.  For example, we will explain in Section \ref{sec:MRFil} that this machinery immediately dispenses with a conjecture of Mahowald and Richter \cite{MahowaldRichter}.  Nonetheless, there are some subtleties involved, and it is these subtleties that prevent us from determining if the Bott filtration is $\mathbb{E}_2$.  The problem is readily visible in the case $n=\infty$:

\begin{exm}\label{exm:BottFil}
The limiting case of the Bott filtration of $\Omega SU(n)$ as $n$ tends to $\infty$ is the filtration
$$* \longrightarrow BU(1) \longrightarrow BU(2) \longrightarrow BU(3) \longrightarrow \cdots \longrightarrow BU \simeq \Omega SU.$$
It is easy to see that $\coprod BU(n)$ is a graded $\mathbb{E}_2$-algebra in spaces (in fact, it is a graded $\mathbb{E}_\infty$-algebra, being the nerve of the category of vector spaces).  However, the filtered object is much more subtle.  For example, the squares
$$
\begin{tikzcd}
BU(i) \times BU(j) \arrow{d} \arrow{r} & BU(i) \times BU(j+1) \arrow{d} \\
BU(i+1) \times BU(j) \arrow{r} & BU(i+1) \times BU(j+1)
\end{tikzcd}
$$
do not commute on the nose, but only up to non-canonical homotopy.
\end{exm}

In Section \ref{sec:FilGra}, we discuss an \textit{associated graded} construction that transforms filtered $\mathbb{E}_n$-algebras into graded $\mathbb{E}_n$-algebras.  Combined with Theorem \ref{thm:BottIsAoo}, this endows the associated graded of the stable Bott filtration with a graded $\mathbb{A}_\infty$-algebra structure.  We may then ask if the associated graded is equivalent to the original spectrum $\Sigma^{\infty}_+ \Omega SU(n)$  as $\mathbb{A}_\infty$ algebras.   This is the main result of our paper, which can be thought of as a multiplicatively structured version of the Mitchell--Richter splitting:

\begin{thm} \label{thm:MainAoo}
As an $\mathbb{A}_\infty$-algebra object in filtered spectra, the Bott filtration of $\Sigma^{\infty}_+ \Omega SU(n)$ is equivalent to its associated graded.
\end{thm}

\begin{cor}
For any multiplicative homology theory $E$, $E_*(\Omega SU(n))$ is a bigraded ring.  One grading is given by $*$, and the other by the associated graded of the Bott filtration.
\end{cor}

In fact, this is the best possible theorem in general:

\begin{thm} \label{thm:MainObstruction}
Suppose $n \ge 4$.  If the Bott filtration of $\Sigma^{\infty}_+ \Omega SU(n)$ may be made into an $\mathbb{E}_2$-algebra object in filtered spectra, then it is \textbf{not} equivalent to its $\mathbb{E}_2$ associated graded.  More generally, any extension of the graded $\mathbb{A}_\infty$-algebra of Theorem \ref{thm:MainAoo} to a graded $\mathbb{E}_2$-algebra must fail to have the usual $\mathbb{E}_2$-algebra structure on its underlying ungraded $\mathbb{E}_2$-ring.
\end{thm}

However, if one is willing to work in a complex-oriented theory such as ordinary homology, the situation improves:

\begin{thm} \label{thm:MainMUE2}
Let $MU$ denote the $\mathbb{E}_\infty$-ring spectrum of complex bordism.  For any $\mathbb{E}_2$-algebra structure on the underlying (ungraded) $\mathbb{A}_\infty$-ring $\gr (\Sigma^{\infty}_+\{F_{n,k}\})$, there is an equivalence of $\mathbb{E}_2$-$MU$-algebras
$$MU \smsh \Sigma^{\infty}_+ \Omega SU(n) \simeq MU \smsh \gr (\Sigma^{\infty}_+\{F_{n,k}\}).$$
\end{thm}

One may now worry that Theorem \ref{thm:MainMUE2} is not very useful if the $\E_2$ filtration of Question \ref{qst:BottE2} is not known; however, it computes the $\E_2$-algebra $MU \smsh \Sigma^{\infty}_+ \Omega SU(n)$ given \emph{any} refinement of $\gr (\Sigma^{\infty}_+\{F_{n,k}\})$ to an $\E_2$ graded spectrum.  This is something that always exists, as we will now illustrate through an example.  

\begin{exm}
In the situation of Example \ref{exm:BottFil}, Theorem \ref{thm:MainAoo} gives an equivalence of $\mathbb{A}_\infty$-ring spectra:
$$\Sigma^{\infty}_+ BU \simeq \bigvee_n \Sigma^{\infty} BU(n)/BU(n-1)$$
where the left-hand side is an $\mathbb{A}_\infty$-algebra by virtue of the fact that $BU$ is a loop space, and the right-hand side inherits its $\mathbb{A}_\infty$-algebra structure as the associated graded of the Bott filtration.  This makes multiplicative an older splitting due to Snaith \cite{SnaithBook}.

%this would be a good place to remark on BU -> MUP; say that noting MU(n) is a thom spectrum ....

This hints at another way to build the $\mathbb{A}_\infty$
\begin{align}\label{eqn:MunSplitting}
\Sigma^{\infty}_+ BU &\simeq \bigvee_n \Sigma^{\infty} BU(n)/BU(n-1) \nonumber \\
 &\simeq \bigvee_n MU(n)
\end{align} 
where $MU(n)$ is the Thom spectrum of the canonical bundle over $BU(n)$, recovering an older splitting due to Snaith \cite{SnaithBook}.  

The left-hand side of (\ref{eqn:MunSplitting}) is an $\mathbb{A}_\infty$-algebra by virtue of the fact that $BU$ is a loop space.  On the other hand, the right-hand side inherits its $\mathbb{A}_\infty$-algebra structure from the Bott filtration.  As it turns out, this latter $\mathbb{A}_\infty$-structure can be constructed another way.  One may construct $\bigvee_n MU(n)$ as a ring spectrum via Thom construction applied to the $J$-homomorphism
$$\coprod BU(n) \stackrel{J}{\longrightarrow} Pic(\mathbb{S}).$$  The right-hand side of (\ref{eqn:MunSplitting}) can then be realized as an $\mathbb{A}_\infty$-algebra by virtue of the fact that the $J$-homomorphism is a loop map.

Of course, $BU$ is not just a loop space, but in fact an infinite loop space.  Similarly, $J$ is not just a loop map, but furthermore an infinite loop map.  Thus, both sides of (\ref{eqn:MunSplitting}) are naturally $\mathbb{E}_\infty$-ring spectra.  Perhaps surprisingly, these $\mathbb{E}_\infty$-rings are \textbf{not} equivalent.
\end{exm}

Though we do not know if the Bott filtration is $\mathbb{E}_2$, in the above example we find a natural graded $\mathbb{E}_2$-algebra structure on its associated graded.  We sketch, at the end of Section \ref{sec:MRFil}, a construction showing that something similar always happens:

\begin{cnstr} \label{cnstr:IntroGr}
Let $\gr (\Sigma^{\infty}_+\{F_{n,k}\})$ denote the associated graded of the Bott filtration of $\Sigma^{\infty}_+ \Omega SU(n)$.  There exists a graded $\mathbb{E}_2$-algebra structure on the graded spectrum $\gr (\Sigma^{\infty}_+ \{F_{n,k}\})$ that extends the canonical graded $\mathbb{A}_\infty$-algebra structure.
\end{cnstr}



\begin{rmk}
As we have seen, it is Construction \ref{cnstr:IntroGr} that gives Theorem \ref{thm:MainMUE2} its teeth.  The result may be seen as a once-looped analogue of work of Kitchloo \cite{Kitchloo}.   Kitchloo studied a splitting, due to Miller \cite{MillerSplitting}, of $\Sigma^{\infty}_+ SU(n)$.  His theorem is that, \textit{for complex-oriented $E$}, the corresponding direct sum decomposition of $E_*(SU(n))$ is multiplicative.
\end{rmk}

Our proof of Theorem \ref{thm:MainMUE2} is by obstruction theory.  We show in Section \ref{sec:MUE2} that all obstructions to an $\mathbb{E}_2$-equivalence vanish.  On the other hand, we prove Theorem \ref{thm:MainObstruction} by explicitly calculating a non-zero obstruction in Section \ref{sec:Obstruction}.  It remains to discuss Theorem \ref{thm:MainAoo}, the $\mathbb{A}_\infty$ splitting of $\Sigma^{\infty}_+ \Omega SU(n)$, which is the central result of our paper.

To prove that a filtered spectrum
$$A_0 \longrightarrow A_1 \longrightarrow A_2 \longrightarrow A_3 \longrightarrow \cdots$$
splits, it suffices to provide splitting maps in the form of a ``cofiltered spectrum''
$$A_0 \longleftarrow A_1 \longleftarrow A_2 \longleftarrow A_3 \longleftarrow \cdots$$
In Section \ref{sec:FilGra} we make this statement precise (with the proof in Appendix \ref{app:SplittingMachine}) by explaining the following theorem:
%Appendix \ref{app:SplittingMachine} we make this statement precise (for rigorous definitions of the terms below, see Section \ref{sec:FilGra}):

\begin{customthm}{\ref{thm:SplitMachine}}%\label{thm:introSplitMachine}%maybe this is an iff 
Let $X\in \Alg_{\E_n}(\Fil(\Sp))$ be an $\E_n$ filtered spectrum.  Suppose there exists an $\E_n$ cofiltered spectrum $Y\in \Alg_{\E_n}(\Cofil(\Sp))$ with the following two properties:
\begin{enumerate}
\item There is an equivalence $\mathrm{colim } X \simeq \lim Y$ of $\E_n$-algebras in spectra.
\item The resulting natural maps $X_i \to Y_i$ are equivalences.  
\end{enumerate}
Then, the filtered spectrum $X$ is $\E_n$-split.
\end{customthm}

We wish to apply this theorem in the case where $X$ is the $\mathbb{A}_\infty$ filtered spectrum in Theorem \ref{thm:BottIsAoo}.  In Section \ref{sec:MultWeiss}, we produce the corresponding $\mathbb{A}_\infty$ cofiltered spectrum; the proof is then finished in Section \ref{sec:AooSplit}.  To do this, we extend the methods of \cite{Arone}, who used Weiss calculus to give an elegant second proof of the Mitchell--Richter splitting (without multiplicative structure).  

Arone's idea is to use additional functoriality present in the filtration of $\Omega SU(n)$.  Let $\J$ denote the topological category of complex vector spaces and embeddings, fix a complex vector space $V$, and consider the functor $$G:\J \longrightarrow \mathcal{S}\text{paces}$$
given by $G(W)=\J(V,V \oplus W)$.  Observe that the special unitary group $SU(V \oplus \mathbb{C})$ arises as the value $G(\mathbb{C}) = \J (V,V\oplus \mathbb{C})$.  Weiss calculus provides a toolbox with which to study functors similar to $G$ -- a brief review of the theory is provided at the beginning of Section \ref{sec:MultWeiss}.  %is the argument actually reviewed?

The Bott filtration in fact arises from a sequence of functors $$F_0(W) \to F_1(W) \to F_2(W) \to \cdots \to F(W) := \Sigma^{\infty}_+ \Omega \J(V, V\oplus W)$$ from $\J$ to spectra.  The crux of Arone's argument is that the Weiss polynomial approximation $P_n F(W)$ is precisely the functor $F_n(W)$ \cite{Arone}.  The approximations $$P_n F(W) \rightarrow P_{n-1} P_n F(W) \simeq P_{n-1} F(W)$$ provide Arone with splitting maps.

To obtain an $\mathbb{A}_\infty$ splitting, it is no longer sufficient to merely provide splitting maps.  As explained by Theorem \ref{thm:SplitMachine}, we instead require an $\mathbb{A}_\infty$ structure on the whole system of splitting maps, considered as a cofiltered spectrum.  This will arise from combining two statements: the first is that the functor $F(W)$ takes values in $\mathbb{A}_\infty$ ring spectra, and thus gives an $\mathbb{A}_\infty$ object in the category $\Sp^{\J}$ of functors from $\J$ to spectra.  The second is that the Weiss tower can be viewed as a symmetric monoidal functor from $\Sp^{\J}$ to cofiltered objects in $\Sp^{\J}$.  This observation, which may be of independent interest, is likely known to experts and was suggested to us by Jacob Lurie, but we could not locate in the literature.  We have proven it in the following form, where $\Sp^{\J}_{\text{conv}}$ denotes restriction to certain conveniently convergent functors:
\begin{customthm}{\ref{thm:weissmonoidal}}
The Weiss tower defines a symmetric monoidal functor $$\text{Tow}: \Sp^{\J}_{\text{conv}} \to \Cofil(\Sp^{\J}_{\text{conv}}).$$
\end{customthm}
\begin{rmk*}
The proof works just as well in the context of Goodwillie calculus (see Remark \ref{rmk:goodwilliecase}).  
\end{rmk*}

There are a number of natural and presumably approachable open questions suggested by our work here.  In addition to Question \ref{qst:BottE2}, we highlight the following:

\begin{qst}
Is the Mitchell--Richter filtration of the loop space of a Stiefel manifold always filtered $\mathbb{A}_\infty$?  This is the only obstruction to promoting Theorem \ref{thm:MainAoo} to a result about all such loop spaces.
\end{qst}

\begin{qst}
What are the proper motivic analogues of our results, phrased in the category of $\mathbb{A}^1$-invariant Nisnevich sheaves?
\end{qst}

\begin{qst}
What are the proper equivariant analogues of our result?  See for example \cite{Ullman}, \cite{Tynan}.
\end{qst}

\subsection*{Acknowledgements}
The authors thank Greg Arone, Lukas Brantner, Denis Nardin, Dennis Gaitsgory, Akhil Mathew, and Haynes Miller for helpful conversations.  We were saddened to learn of the passing of Steve Mitchell during the preparation of this manuscript--his papers were a deep inspiration.  Special thanks are due to the authors' PhD advisors, Mike Hopkins and Jacob Lurie, both for their mathematical expertise and their consistent encouragement; many of the ideas in this paper grew out of their suggestions.  Special thanks are also due to Justin Campbell, James Tao, David Yang, and Yifei Zhao, all of whom spent numerous and invaluable hours answering naive questions about the Beilinson--Drinfeld Grassmannian.  The authors were supported by NSF Graduate Fellowships under Grants DGE-114415 and 1122374.

\subsection*{Notation:} We use $\Sp$ to denote the category of spectra, and $\mathcal{S}$ the category of spaces.  As through the introduction, we will freely use the word category to refer to a not-necessarily truncated $\infty$-category.
